---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# jordan

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/jmbarbone/jordan.svg?branch=master)](https://travis-ci.com/jmbarbone/jordan)
<!-- badges: end -->

**j**ust **o**ther **R** **d**ata **a**nalytic **n**uggets

An R package with a set of general use functions for data analytics.
This is developed mostly for personal use and has no real _goal_ other than to limit the time I spend searching where I did that thing that I think I could use again because it worked well but this problem might be slightly different and I know I had to change it before.

Some parts happily ripped from and (hopefully) credited to others.

## Installation

You can the development version from [GitHub](https://github.com/jmbarbone/jordan) with:

```
devtools::install_github("jmbarbone/jordan")
```

## Select examples

This package contains a many variety of functions, some useful, some not so much.
Below are a selection of a few functions that could potential be useful for others:

```{r library}
library(jordan)
```

Get dates from sloppy entries:

```{r dates}
bad_dates <- c("2020 Dec 8th", "1970 May", "??", "1984 UNK UN")
date_from_partial(bad_dates)
date_from_partial(bad_dates, method = "max")
date_from_partial(c("May 2000", "08Dec2020"), format = "dmy")
```

Slice strings:

```{r strings}
x <- stringi::stri_rand_lipsum(1)
str_slice(x, n = 50L)
str_slice_by_word(x)
```

Read in bibliographies:

```{r bibs}
file <- "https://raw.githubusercontent.com/jmbarbone/bib-references/master/references.bib"
bib <- read_bib(file)
tibble::as_tibble(bib)
```

More matching:

```{r matching}
1:10 %out% c(1, 3, 5, 9) # opposite of %in% 
letters[1:5] %wo% letters[3:7]
letters[1:5] %wi% letters[3:7]
```

