---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# jordan

<!-- badges: start -->
<!-- badges: end -->

**J**ust **O**ther **R** **D**ata **A**nalytic **N**uggets

An R package with a set of general use functions for data analytics.
This is developed mostly for personal use and has no real _goal_ other than to limit the time I spend searching where I did that thing that I think I could use again because it worked well but this problem might be slightly different and I know I had to change it before.

Some parts happily ripped from and (hopefully) credited to others.

## Installation

You can the development version from [GitHub](https://github.com/jmbarbone/jordan) with:

``` r
remotes::install_github("jmbarbone/jordan")
```
## Example

~~We're~~ I'm still working on this...

```{r example}
library(jordan)
```


